### 2016-10-02 comparison_with_mma.tex
or -> "overloadability of the functionality" ?

In[3]:= x + Sin[t]^2 + y + Cos[t]^2
Out[3]= 1 + x + y
\end{verbatim}
This expression in Mathematica defines a substitution rule that overloads
the functionality of the \texttt{Plus} node (the node for additions in Mathematica).
A symbol with a trailing underscore is treated as a wildcard.
Although one may wish to keep this identity unevaluated, this example clearly
illustrates the potential to define
one's own immediate transformation rules.
In SymPy, the operations constructing the addition node in the expression tree
are Python class constructors
and cannot be modified at runtime.\footnote{Python does support monkey
patching, but it is a discouraged programming pattern.}
The way SymPy deals with extending the missing runtime overloadability functionality
is by subclassing the node types: subclasses may redefine the class constructor
to yield the proper extended functionality.

>>>>

In[3]:= x + Sin[t]^2 + y + Cos[t]^2
Out[3]= 1 + x + y
\end{verbatim}
This expression in Mathematica defines a substitution rule that overloads
the functionality of the \texttt{Plus} node (the node for additions in Mathematica).
A symbol with a trailing underscore is treated as a wildcard.
Although one may wish to keep this identity unevaluated, this example clearly
illustrates the potential to define
one's own immediate transformation rules.
In SymPy, the operations constructing the addition node in the expression tree
are Python class constructors
and cannot be modified at runtime.\footnote{Python does support monkey
patching, but it is a discouraged programming pattern.}
The way SymPy deals with extending the missing runtime overloadability
is by subclassing the node types: subclasses may redefine the class constructor
to yield the proper extended functionality.
